### 2021-12-24 paper/manuscript.Rmd
start standardization

author:
  - name: "Caspar J. Van Lissa"
    affiliation: "1,2"
    corresponding: yes
    address: "Padualaan 14, 3584CH Utrecht, The Netherlands"
    email: "c.j.vanlissa@uu.nl"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Writing - Original Draft Preparation
      - Programming front-end
  - name: "Sara van Erp"
    affiliation: "1"
    role:
      - Writing - Contributions and feedback
      - Programming back-end
affiliation:
  - id            : "1"
    institution   : "Utrecht University, dept. Methodology & Statistics"
  - id            : "2"
    institution   : "Open Science Community Utrecht"

@@

>>>>

author:
  - name: "Caspar J. Van Lissa"
    affiliation: "1,2"
    corresponding: yes
    address: "Padualaan 14, 3584CH Utrecht, The Netherlands"
    email: "c.j.vanlissa@uu.nl"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Writing - Original Draft Preparation
      - Programming front-end
  - name: "Sara van Erp"
    affiliation: "1"
    role:
      - Writing - Contributions and feedback
      - Programming back-end
  - name: "Eli-Boaz Clapper"
    affiliation: "1"
affiliation:
  - id            : "1"
    institution   : "Utrecht University, dept. Methodology & Statistics"
  - id            : "2"
    institution   : "Open Science Community Utrecht"

@@

In Lasso regression it is often preferred to equalize the scales of the predictors (REF). This is because $\lambda$, the regularization parameter, constrains the absolute magnitude of the coefficients that are dependent on the scales of the predictors. This leads to Lasso unfairly penalizing large coefficients that do not necessarily reflect importance (REF).
Equalizing scales is usually done by setting the mean of all predictors to 0 and their variance to 1, a procedure known as standardization. This procedure transforms all elements in a predictor vector to Z-scores as follows:
$\boldsymbol{Z} = \frac{\boldsymbol{X} - \mu_\boldsymbol{X}}{\sigma_\boldsymbol{X}}$
where $\boldsymbol{X}$ is the vector of the predictor, $\mu_\boldsymbol{X}$ is its mean and $\sigma_\boldsymbol{X}$ is its standard deviation.
